### 2024-02-01 paper.tex
change order, less confusing

\noindent%
\begin{minipage}{\linewidth}
	\begin{center}
	    \includegraphics[width=\textwidth]{figures/SFig_benchmark.png}
	\end{center}
	\captionof{figure}{\small \new{ \textbf{Benchmark of several combinations of analysis methods on four single-cell methylation data sets.}\\
	\textbf{(A-E)} Benchmarking the ability to separate groups of cells based on CpG methylation data, using different analysis approaches.
	Methylation matrices were obtained either by averaging CpG methylation in genomic intervals (dotted lines, hollow points) or using the shrunken mean of residuals (solid lines and points).
	Each analysis was performed for the full data sets and sub-samples of each.
	Four sets of genomic intervals (VMRs, ENCODE regulatory elements, 100~kb tiles or promoters) were quantified and separately subjected to four dimensionality reduction techniques (see Methods for details):
	iterative PCA as proposed by us, mean-imputed PCA on intervals with high sequencing coverage \citep{luo2017single}, mean-imputed PCA on all intervals, and MOFA+ \citep{argelaguet2020mofa} on all intervals.
	For each combination of methods, we quantified the ability to use distance in 15-dimensional PCA space to separate ground-truth cell labels reported by the authors (neighbor score).
	\textbf{(A)} Separation of neural cell types/states annotated based on scRNA-seq of the same cells \citep{kremer_scnmt}.
	\textbf{(B)} Separation of neuron sub-types, annotated by averaging CH-methylation (mCH) in 100~kb genomic tiles \citep{luo2017single}.
	\textbf{(C)} Separation of human colorectal cancer sampling regions (normal adjacent tissue, primary tumor, lymph node metastasis, liver metastasis before and after treatment, omental metastasis) \citep{bian2018single}.
	\textbf{(D-E)} Separation of three properties of mouse embryo cells:
	The developmental stage (E4.5, E5.5, E6.5, E7.5), the germ layer or extra-embryonic tissue of origin, or the cell lineage.
	Germ layer and lineage (\textbf{E}, only E7.5-cells) were annotated by \citet{argelaguet2019gastru} based on scRNA-seq of the same cells.
	}}
	\label{fig:score_luo}

>>>>

\noindent%
\begin{minipage}{\linewidth}
	\begin{center}
	    \includegraphics[width=\textwidth]{figures/SFig_benchmark.png}
	\end{center}
	\captionof{figure}{\small \new{ \textbf{Benchmark of several combinations of analysis methods on four single-cell methylation data sets.}\\
	\textbf{(A-E)} Benchmarking the ability to separate groups of cells based on CpG methylation data, using different analysis approaches.
	Methylation matrices were obtained either by averaging CpG methylation in genomic intervals (dotted lines, hollow points) or using the shrunken mean of residuals (solid lines and points).
	Each analysis was performed for the full data sets and sub-samples of each.
	Four sets of genomic intervals (VMRs, ENCODE regulatory elements, 100~kb tiles or promoters) were quantified and separately subjected to four dimensionality reduction techniques (see Methods for details):
	iterative PCA as proposed by us, mean-imputed PCA on intervals with high sequencing coverage \citep{luo2017single}, mean-imputed PCA on all intervals, and MOFA+ \citep{argelaguet2020mofa} on all intervals.
	For each combination of methods, we quantified the ability to use distance in 15-dimensional PCA space to separate ground-truth cell labels reported by the authors (neighbor score).
	\textbf{(A)} Separation of neural cell types/states annotated based on scRNA-seq of the same cells \citep{kremer_scnmt}.
	\textbf{(B)} Separation of neuron sub-types, annotated by averaging CH-methylation (mCH) in 100~kb genomic tiles \citep{luo2017single}.
	\textbf{(C)} Separation of human colorectal cancer sampling regions (primary tumor, normal adjacent tissue, lymph node metastasis, liver metastasis before and after treatment, omental metastasis) \citep{bian2018single}.
	\textbf{(D-E)} Separation of three properties of mouse embryo cells:
	The developmental stage (E4.5, E5.5, E6.5, E7.5), the germ layer or extra-embryonic tissue of origin, or the cell lineage.
	Germ layer and lineage (\textbf{E}, only E7.5-cells) were annotated by \citet{argelaguet2019gastru} based on scRNA-seq of the same cells.
	}}
	\label{fig:score_luo}
